\documentclass[11pt, aspectratio=169]{beamer}
\usefonttheme[onlymath]{serif}

\setbeamersize{text margin left=1.5em}
\setbeamersize{text margin right=1.5em}

\setbeamertemplate{frametitle}{%
  \vskip1ex
  \usebeamerfont{frametitle}%
  \insertframetitle\par
  \vskip1ex
  \hrule
}

\setbeamertemplate{blocks}[rounded][shadow=true]

\setbeamertemplate{itemize item}{\usebeamerfont{itemize item}\textbullet}
\setbeamertemplate{itemize subitem}{\usebeamerfont{itemize subitem}\textbullet}
\setbeamertemplate{itemize subsubitem}{\usebeamerfont{itemize subsubitem}\textbullet}

\makeatletter
\geometry{%
  papersize={\fpeval{\beamer@paperwidth*1.4}pt,\fpeval{\beamer@paperheight*1.4}pt},
  hmargin=\fpeval{0.5 * 1.0}cm,% 1cm
  vmargin=0cm,%
  head=\fpeval{0.5*1.4}cm,% 0.5cm
  headsep=0pt,%
  foot=\fpeval{0.5*1.4}cm% 0.5cm
}
\makeatother

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}

\usepackage[
  backend=bibtex,
  style=authoryear,   % or numeric
  citestyle=authoryear
]{biblatex}
\addbibresource{../../references.bib}

% Your custom commands (kept as is)
\newcommand{\mrm}[1]{\mathrm{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\tb}[1]{\textbf{#1}}
\newcommand{\Unif}{\operatorname{Unif}}

\title{Improvement Conservative Q Learning}
\author{Gwanwoo Choi}
\institute{MLIC}
\date{} % To use the current date

\begin{document}

\begin{frame}
    \titlepage
\end{frame}


% https://tex.stackexchange.com/questions/541559/citep-vs-parencite
% \citep - \parencite
% \citet - \textcite
% \citealp - \citealt - \cite


\begin{frame}{Offline Learning}
  \begin{block}{Preliminaries of Offline Reinforcement Learning}
    \itemize{
        \item Markov Decision Process (MDP): $(\mc{S}, \mc{A}, p, r, \gamma)$
        \item State space: $\mc{S}$, Action space: $\mc{A}$
        \item Transition dynamics: $p(s^\prime|s,a)$, Reward function: $r(s,a)$
        \item Discount factor: $\gamma \in [0,1)$
        \item Policy: $\pi(a|s)$, Behavior Policy: $\beta(a|s)$
        \item In offline RL, we cannot interact with environment during training. Only have static dataset $\mc{D} = \{(s_i, a_i, r_i, s_i^\prime)\}_{i=1}^N$ collected by unknown behavior policy $\beta$.
        \item Goal: Find optimal policy $\pi^*$ that maximize cumulative discounted reward in \tb{test time}.
        $$J(\pi) = \mbb{E}_{\substack{s_0 \sim p_0 \\ a_t \sim \pi(\cdot|s_t) \\ s_{t+1} \sim p(\cdot|s_t,a_t)}}\left[\sum_{t=0}^\infty \gamma^t r(s_t,a_t)\right]$$
    }
  \end{block}
  % }
\end{frame}

\begin{frame}{Offline Learning}
    \begin{block}{Problem of Offline RL}
    \itemize{
        \item Offline RL: Learn policy from static dataset $\mc{D}$ collected by unknown behavior policy $\beta$.
        \item In offline learning, we can not know the real transition dynamics $p(s^\prime|s,a)$. So critic learning is occured only on the points of \tb{in-distribution} $(s,a)$ state-action pair of dataset $\mc{D}$.
        $$
          \min_\theta \mbb{E}_{\substack{(s,a,r,s^\prime) \sim \mc{D} \\ a^\prime \sim \pi_\phi} }\left[ (r + \gamma Q_\theta(s^\prime, a^\prime)  - Q_\theta (s,a))^2\right]
        $$

        \item One of the problem of Offline RL is \tb{unseen state-action pairs} $(s,a) \sim \pi$ lead to errors due to untrustworthy function approximation. 
        
        \item In offline RL, not all state-action points may be included in the dataset $\mc{D}$, forcing the $Q$ function to extrapolate. This can cause large errors that accumulate through the Bellman update:
        $$
          \min_\theta \mbb{E}_{\substack{(s,a,r,s^\prime) \sim \mc{D} \\ \textcolor{red}{a^\prime \sim \pi_\phi}} }\left[ (r + \gamma \textcolor{red}{Q_\theta(s^\prime, a^\prime)}  - Q_\theta (s,a))^2\right]
        $$
    }
  \end{block}
\end{frame}

\begin{frame}{Out-of-Distribution Problem}
    \begin{block}{OOD problem}
      Suppose we learn $Q$ function by Soft Actor Critic, which is online algorithm, in \tb{offline setting}.
      \begin{itemize}
        \item The objective of SAC is to minimize the following loss:
        $$
        \begin{gathered}
        \textcolor{violet}{\min_\phi} \mbb{E}_{\substack{s \sim \mc{D} \\ a \sim \pi_\phi}}\left[\alpha \log \pi_\phi(a|s) \textcolor{violet}{- Q_\theta(s,a)}\right] \\
        \min_\theta \mbb{E}_{\substack{(s,a,r,s^\prime) \sim \mc{D} \\ \textcolor{red}{a^\prime \sim \pi_\phi}} }\left[ (r + \gamma \textcolor{red}{Q_\theta(s^\prime, a^\prime)}  - Q_\theta (s,a))^2\right]
        \end{gathered}
        $$
        \item \tb{Key question}: Is $\textcolor{red}{Q_\theta (s^\prime, a^\prime)}$ reliable when $(s^\prime, a^\prime)$ is \textcolor{red}{out-of-distribution}?
        \item If $(s^\prime, a^\prime)$ is OOD, $Q_\theta(s^\prime, a^\prime)$ is often \tb{overestimated} due to extrapolation.
        \item This overestimation propagates: $Q(s,a) \leftarrow r + \gamma Q(s^\prime, a^\prime)$, compounding errors.
        \item The policy then exploits \textcolor{violet}{overestimated Q-values}, selecting poor actions that appear artificially good.


        % \item Is $\textcolor{red}{Q_\theta (s^\prime, a^\prime)}$ trustworthy? What if $(s^\prime, a^\prime)$ is \textcolor{red}{out-of-distribution}?
        % \item Suppose that, unfortunately, $Q(s^\prime, a^\prime)$ is \tb{highly approximated} for an OOD point $(s^\prime, a^\prime)$.
        % \item Then this overestimation error propagates through bootstrapping: $Q(s,a) \leftarrow r + \gamma Q(s^\prime, a^\prime)$.
        % \item Also, \textcolor{violet}{overestimated $Q$} values lead to suboptimal policy updates in the policy improvement step. \textcolor{gray}{(why?)}
        % % \item If $(s^\prime, a^\prime)$ is OOD, then $Q_\theta(s^\prime, a^\prime)$ tends to be \tb{overestimated} due to extrapolation errors in function approximation. The policy $\pi_\phi$ then exploits these overestimated values, leading to performance degradation.
      \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Conservative Q Learning}
  \begin{block}{Conservative Q Learning \parencite{kumarConservativeQLearningOffline2020} Motivation}
    
    \tb{Goal}: Prevent overestimation by making Q-values \tb{conservative} for OOD actions.
    % \tb{Key question}: Is $\textcolor{red}{Q_\theta (s^\prime, a^\prime)}$
    % How can we solve the OOD \& overestimation problem?
    \begin{itemize}
      \item \tb{Key insight}: Actions from policies different from $\beta$ are more likely to be OOD.
      \item Consider an arbitrary policy $\mu \neq \beta$. For $s \sim \mc{D}$ and $a \sim \mu(\cdot|s)$, the pair $(s,a)$ may be OOD.
      \item \tb{Approach(1)}: Lower Q-values for actions under $\mu$ while keeping them accurate for actions in $\mc{D}$:
      \item \tb{Objective(1)}: Penalize Q-values for actions sampled from $\mu$:
      \begin{equation}
        \min_\theta \max_\mu  \underbrace{\alpha \mbb{E}_{\substack{s \sim \mc{D} \\ a \sim \mu}}\left[Q_\theta(s,a)\right]}_{\text{Conservatism penalty}} + \underbrace{\frac{1}{2}\mbb{E}_{\substack{(s,a,r,s^\prime) \sim \mc{D} \\ a^\prime \sim \pi_\phi}}\left[\left(r + \gamma Q_\theta(s^\prime, a^\prime) - Q_\theta(s,a)\right)^2\right]}_{\text{Standard Bellman error}} + \underbrace{\mc{R}(\mu)}_{\text{Regularizer on } \mu}
      \end{equation}
        % \min_\theta \max_\mu \left\{ \alpha \mbb{E}_{s \sim \mc{D}, a \sim \mu}[Q_\theta(s,a)] - \mbb{E}_{(s,a) \sim \mc{D}}[Q_\theta(s,a)] \right\}
      \item This encourages conservative Q-estimates for OOD actions.
      \item But this objective \tb{can hurt Q-values for in-distribution actions} $a \in \mc{D}$.
      \item \tb{Approach(2)}: Do not penalize Q-values for in-distribution actions.
      \item \tb{Objective(2)}: Depenalize Q-values for in-distribution actions:
      \begin{equation}
          \min_\theta \max_\mu  \underbrace{\alpha \left(\mbb{E}_{\substack{s \sim \mc{D} \\ a \sim \mu}}\left[Q_\theta(s,a)\right] - \mbb{E}_{(s,a) \sim \mc{D}}[Q_\theta(s,a)]\right)}_{\text{More loosen conservatism penalty}} + \underbrace{\frac{1}{2}\mbb{E}_{\substack{(s,a,r,s^\prime) \sim \mc{D} \\ a^\prime \sim \pi_\phi}}\left[\left(r + \gamma Q_\theta(s^\prime, a^\prime) - Q_\theta(s,a)\right)^2\right]}_{\text{Standard Bellman error}} + \underbrace{\mc{R}(\mu)}_{\text{Regularizer on } \mu}
      \end{equation}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Conservative Q Learning}
  \begin{block}{Conservative Q Learning Framework}
    \begin{itemize}
      \item \tb{Policy Evaluation}: Learn conservative Q-function by minimizing the CQL objective:
      $$
        \min_\theta \max_\mu  \alpha \left(\mbb{E}_{\substack{s \sim \mc{D} \\ a \sim \mu}}\left[Q_\theta(s,a)\right] - \mbb{E}_{(s,a) \sim \mc{D}}[Q_\theta(s,a)]\right) + \frac{1}{2}\mbb{E}_{\substack{(s,a,r,s^\prime) \sim \mc{D} \\ a^\prime \sim \pi_\phi}}\left[\left(r + \gamma Q_\theta(s^\prime, a^\prime) - Q_\theta(s,a)\right)^2\right] + \mc{R}(\mu)
      $$
      \item \tb{Policy Improvement}: Update policy via maximizing expected Q-values:
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Idea}
    \itemize{
        \item More generalize for unseen state. In policy learning, sampling not only $s$, but also $s^{\prime}$. Add maximize term $\max_V \mbb{E}_{s \sim \mc{D}}[V(s)] = \mbb{E}_{s \sim \mc{D}, a \sim \pi^k, a^\prime \sim \operatorname{Unif}}[Q(s,a) - \log \pi(a^\prime|s)]$ of CQL policy evaluation. Want to maximize value function for seen state $s \sim \mc{D}$.
        \item Modify Penalize term (current is $Q^\pi(s,a) \leftarrow \mc{B}^\pi Q^\pi(s,a) -\alpha \lvert \frac{\mu(a|s)}{\beta(a|s)} -1 \rvert$. What if this term changes action sampling N $a_1, a_2, \dots, a_N \sim \mu(\cdot|s)$ and $\sum_n \lvert a_n - a \rvert^2 /N$). This approach wants to basically wasserstein-2 distance of Flow Q Learning. Note that target domain is continuous control. And also, CQL implementation set $\mu$ not uniform distribution, instead mixed density of policy $\pi$ and $\mu$.
    }
\end{frame}

\begin{frame}
    \frametitle{References}
    \printbibliography
\end{frame}

\end{document}

